Priors

### 2024-03-07 analysis/clinical-data.Rmd
Update plots
Modeling fixes and visual updates

```{r}
diag_tb <- df %>%
  mutate(
    date_in_model = format(as.Date(date), format = "%b %d"),
    date_in_model = ifelse(
      date_in_model %in% modeled_days_abbrv, date_in_model,
      "Not modeled"
    ),
    date_in_model = factor(
      date_in_model,
      levels = c(modeled_days_abbrv, "Not modeled")
    )
  ) %>%
  group_by(date, date_in_model) %>%
  summarize(
    n_infectious = sum(is_infectious),
    n_suspected = sum(was_suspected & !is_infectious)
  ) %>%
  ungroup() %>%
  reshape2::melt(c("date", "date_in_model")) %>%
  mutate(
    variable = ifelse(grepl("infectious", variable), "Diagnosed", "Suspected"),
    variable = factor(variable, levels = c("Suspected", "Diagnosed"))
  )

@@

save_plot(
  diag_tb_pl,
  pdf_file = "results/data/diagnosed-tb-patients.png",
  w = 16, h = 12
)
```

@@

table(diag_tb$value[diag_tb$variable == "Diagnosed"])

#' Assumption:
#' Number of diagnosed ~ number of diagnosed TB
#' --> Assume a Dirichlet prior with support according to the counts in the range (1,5).

source("utils/trans_risk.r")

undiag_tb_pl <- data.frame(x = rundiag(1e5)) %>%
  group_by(x) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(
    p = 100 * n / sum(n),
    p = round(p)
  ) %>%
  ggplot(aes(x = factor(x), y = p)) +
  geom_bar(
    stat = "identity",
    color = wes_palette("GrandBudapest1")[3],
    fill = wes_palette("GrandBudapest1")[4],
    alpha = .5
  ) +
  labs(
    x = "Number of undiagnosed TB patients", y = "Probability (%)"
  ) +
  coord_cartesian(expand = F) +
  scale_y_continuous(limits = c(0, NA)) +
  theme_custom(8) +
  theme(plot.caption = element_text(size = 10))

>>>>

```{r}
diag_tb <- df %>%
  mutate(
    date_in_model = format(as.Date(date), format = "%b %d"),
    date_in_model = ifelse(
      date_in_model %in% modeled_days_abbrv, date_in_model,
      "Not modeled"
    ),
    date_in_model = factor(
      date_in_model,
      levels = c(modeled_days_abbrv, "Not modeled")
    )
  ) %>%
  group_by(patient_id, date) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(date, date_in_model) %>%
  summarize(
    n_infectious = sum(is_infectious),
    n_suspected = sum(was_suspected & !is_infectious)
  ) %>%
  ungroup() %>%
  reshape2::melt(c("date", "date_in_model")) %>%
  mutate(
    variable = ifelse(grepl("infectious", variable), "Diagnosed", "Suspected"),
    variable = factor(variable, levels = c("Suspected", "Diagnosed"))
  )

diag_tb %>%
  filter(date_in_model != "Not modeled") %>%
  group_by(variable) %>%
  summarise(sum(value))

@@

save_plot(
  diag_tb_pl,
  pdf_file = "results/data/diagnosed-tb-patients.png",
  w = 16, h = 10
)
```

@@

counts <- table(diag_tb$value[diag_tb$variable == "Diagnosed"])
counts
df_counts <- data.frame(
  x = names(counts),
  n = as.numeric(counts),
  p = round(100 * as.numeric(counts) / sum(counts))
)

undiag_tb_pl <- df_counts %>%
  ggplot(aes(x = factor(x), y = p)) +
  geom_bar(
    stat = "identity",
    color = "grey0",
    fill = "grey70",
    alpha = .8
  ) +
  geom_text(
    aes(label = paste0("n" = n, " (", p, "%)")),
    vjust = -1,
    size = 8 / cm(1)
  ) +
  labs(
    x = "Number of undiagnosed TB patients", y = "Probability (%)"
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, .12))) +
  theme_custom(8) +
  theme(plot.caption = element_text(size = 10))

### 2024-03-07 analysis/patient-tracking.Rmd
Modeling fixes and visual updates

# filter considered clinical attendees
df_matched <- do.call(
  rbind,
  lapply(
    unique(df$date),
    function(d) {
      readRDS(paste0(
        "data-clean/patient-tracking/matched-clinical/",
        d, ".rds"
      ))
    }
  )
) %>%
  mutate(date = as.Date(time))
df_filt <- filter(
  df,
  paste(date, patient_id) %in%
    unique(paste(df_matched$date, df_matched$patient_id))
)
```

@@

```{r}
n_distinct(paste(df$date, df$patient_id))
n_distinct(paste(df_filt$date, df_filt$patient_id))
```

>>>>

# filter considered clinical attendees
df_matched <- do.call(
  rbind,
  lapply(
    unique(df$date),
    function(d) {
      readRDS(paste0(
        "data-clean/patient-tracking/matched-clinical/",
        d, ".rds"
      ))
    }
  )
) %>%
  mutate(
    date = as.Date(time),
    hr = lubridate::hour(time)
  ) %>%
  filter(between(hr, 8, 15)) %>%
  filter(!(hr > 11 & date == "2021-10-15")) %>%
  group_by(date, patient_id) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(patient_id = paste(date, patient_id))

df_filt <- filter(
  df,
  paste(date, patient_id) %in% df_matched$patient_id
)
```

@@

```{r}
n_distinct(paste(df$date, df$patient_id))
n_distinct(paste(df_filt$date, df_filt$patient_id))
df_filt %>%
  filter(tracking_end != "Possible HCW") %>%
  mutate(patient_id = paste(date, patient_id)) %>%
  dplyr::select(patient_id) %>%
  n_distinct()
```

### 2024-03-07 analysis/qctr.Rmd
Modeling fixes and visual updates

@@

  average_tr <- tr %>%
    mutate(patient_id = paste(mthdy, patient_id, sep = "-")) %>%
    group_by(patient_id) %>%
    summarize(
      P_mean = mean(P),
      P_med = median(P)
    ) %>%
    ungroup() %>%
    left_join(track %>%
      mutate(
        mth = lubridate::month(time),
        dy = lubridate::day(time)
      ) %>%
      group_by(patient_id, mth, dy) %>%
      slice(1) %>%
      ungroup() %>%
      mutate(dy = ifelse(nchar(dy) == 1, paste0("0", dy), dy)) %>%
      mutate(patient_id = paste(
        mth, dy,
        patient_id,
        sep = "-"
      )) %>%
      dplyr::select(patient_id, tracking_end)) %>%
    filter(tracking_end != "Possible HCW") %>%
    dplyr::select(-tracking_end) %>%
    reshape2::melt("patient_id") %>%
    mutate(
      val_col = ifelse(value < .05, "Low",
        ifelse(value < .1, "Median", "High")
      ),
      val_col = factor(val_col, levels = c("Low", "Median", "High")),
      variable = ifelse(
        grepl("mean", variable),
        "Mean risk of infection",
        "Median risk of infection"
      ),
      variable = factor(
        variable,
        levels = paste(c("Mean", "Median"), "risk of infection")
      )
    )

@@

@@

@@

annon_comp <- rbind(
  nm_annon %>% mutate(scenario = "No mask wearing"),
  vent_annon %>% mutate(scenario = "Lower ventilation"),
  prev_annon %>% mutate(scenario = "Prevalence-based model"),
  susp_annon %>% mutate(scenario = "Suspected-based model")
) %>%
  mutate(
    scenario = factor(scenario, levels = c(
      "No mask wearing",
      "Lower ventilation",
      "Prevalence-based model",
      "Suspected-based model"
    ))
  )

@@

@@

mod_comp_pl <- mod_comp %>%
  ggplot(aes(x = diff)) +
  geom_histogram(
    mapping = aes(fill = val_col),
    binwidth = .005,
    boundary = 1
  ) +
  geom_text(
    data = mod_comp_annon,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  labs(
    y = "Number of clinical attendees (log-scale)",
    x = "Difference between spatiotemporal and temporal model (perc. points)"
  ) +
  scale_y_log10(labels = scales::comma) +
  scale_x_continuous(labels = function(x) scales::percent(x, suffix = "")) +
  scale_fill_manual(values = wes_palette("Zissou1")[c(1, 3, 5)]) +
  coord_cartesian(expand = FALSE) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm")
  )

>>>>

# example translation
source("utils/trans_risk.r")
IR_sit <- .5 * IR("sitting", "male") + .5 * IR("sitting", "female")
WR_vol <- convert_dist(cellSize)^2 * dimWR[3]
round((1 - exp(-max(main_qc_wr_mo$value) * 600 * IR_sit / WR_vol)) * 100, 0)
round((1 - exp(-max(main_qc_wr_af$value) * 600 * IR_sit / WR_vol)) * 100, 0)

@@

  average_tr <- tr %>%
    mutate(patient_id = paste(mthdy, patient_id, sep = "-")) %>%
    group_by(patient_id) %>%
    summarize(
      P_mean = mean(P),
      P_med = median(P)
    ) %>%
    ungroup() %>%
    left_join(track %>%
      mutate(
        mth = lubridate::month(time),
        dy = lubridate::day(time)
      ) %>%
      group_by(patient_id, mth, dy) %>%
      slice(1) %>%
      ungroup() %>%
      mutate(dy = ifelse(nchar(dy) == 1, paste0("0", dy), dy)) %>%
      mutate(patient_id = paste(
        mth, dy,
        patient_id,
        sep = "-"
      )) %>%
      dplyr::select(patient_id, tracking_end)) %>%
    filter(tracking_end != "Possible HCW") %>%
    dplyr::select(-tracking_end) %>%
    reshape2::melt("patient_id") %>%
    mutate(
      val_col = ifelse(value < .05, "Low",
        ifelse(value < .1, "Medium", "High")
      ),
      val_col = factor(val_col, levels = c("Low", "Medium", "High")),
      variable = ifelse(
        grepl("mean", variable),
        "Mean risk of infection",
        "Medium risk of infection"
      ),
      variable = factor(
        variable,
        levels = paste(c("Mean", "Medium"), "risk of infection")
      )
    )

@@

main_tr %>%
  filter(variable == "Mean risk of infection") %>%
  group_by(val_col) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(prop = round(n / sum(n) * 100, 0))

@@

amod_est %>%
  group_by(variable) %>%
  summarize(
    lower = quantile(value, .025),
    median = median(value),
    upper = quantile(value, .975)
  ) %>%
  mutate(across(c(lower, median, upper), ~ round_k(.x, 2)))

@@

annon_comp <- rbind(
  nm_annon %>% mutate(scenario = "No mask wearing"),
  vent_annon %>% mutate(scenario = "Lower ventilation"),
  prev_annon %>% mutate(scenario = "Prevalence-based model"),
  susp_annon %>% mutate(scenario = "Suspected-based model")
) %>%
  mutate(
    scenario = factor(scenario, levels = c(
      "No mask wearing",
      "Lower ventilation",
      "Suspected-based model",
      "Prevalence-based model"
    ))
  )

@@

mod_comp %>%
  filter(variable == "Mean risk of infection") %>%
  group_by(val_col) %>%
  summarize(n = n()) %>%
  mutate(prop = round(n / sum(n) * 100, 0))

@@

mod_comp_pl <- mod_comp %>%
  ggplot(aes(x = diff)) +
  geom_histogram(
    mapping = aes(fill = val_col),
    binwidth = .005,
    boundary = 1
  ) +
  geom_text(
    data = mod_comp_annon,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  labs(
    y = "Number of clinical attendees",
    x = "Difference between spatiotemporal and temporal model (perc. points)"
  ) +
  scale_y_log10(labels = scales::comma) +
  scale_x_continuous(labels = function(x) scales::percent(x, suffix = "")) +
  scale_fill_manual(values = wes_palette("Zissou1")[c(1, 3, 5)]) +
  coord_cartesian(expand = FALSE) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm")
  )

### 2024-03-07 illustrations/priors.Rmd
Modeling fixes and visual updates

q_dat %>%
  group_by(activity) %>%
  tidybayes::median_qi(x, .width = .5)

@@

lambda_dat %>%
  tidybayes::median_qi(x, .width = .5)

>>>>

q_dat %>%
  group_by(activity) %>%
  tidybayes::median_qi(x, .width = .95) %>%
  mutate_if(is.numeric, round, 3)

@@

lambda_dat %>%
  tidybayes::median_qi(x) %>%
  mutate_if(is.numeric, round, 1)
